7_cluster_figs

### 2018-03-28 7_cluster_figs.Rmd
final cluster figs

knitr::read_chunk('R/utils.R')

# source('R/utils.R')
```

```{r utils}
```

@@

s <- s_clust_map(m, tracts, data, blocked_tracts, size_coef = 1)
s

@@

h <- h_clust_map(m, blocked_tracts, blocked_data, a, j, size_coef = 1)
h

@@

```{r}
f <- h_clust_map(m, tracts, data, b, j, size_coef = 1)
f
ggsave(paste0('figs/hclust_', city,'.pdf'), width = map_width, height = map_height)
```

@@

b <- h_clust(tracts, data)
```

@@

```{r}
k     <- 36
g     <- spectral_cluster(g, sigma = sigma, k = k, nreps = 1000)
```

@@

h <- h_clust_map(m, blocked_tracts, blocked_data, a, j, size_coef = 1)

@@

```{r}
city    <- 'Philadelphia'
in_data <- read_data(city, all_data)
data    <- in_data$data
tracts  <- in_data$tracts
```

@@

h <- h_clust_map(m, blocked_tracts, blocked_data, a, j, size_coef = 1)
h
ggsave(paste0('figs/mixed_', city,'.pdf'), width = map_width, height = map_height)
```

```{r}
f <- h_clust_map(m, tracts, data, b, j, size_coef = 1)
f
ggsave(paste0('figs/hclust_', city,'.pdf'), width = map_width, height = map_height)
```

@@

<!-- # Dallas -->

<!-- ```{r} -->
<!-- city    <- 'Dallas' -->
<!-- in_data <- read_data(city, all_data) -->
<!-- data    <- in_data$data -->
<!-- tracts  <- in_data$tracts -->
<!-- ``` -->

<!-- ## Filter out the small island -->
<!-- ```{r} -->
<!-- g <- construct_information_graph(tracts = tracts,  -->
<!-- 								 data = data,  -->
<!-- 								 divergence = euc) -->

<!-- comps <- igraph::components(g) -->

<!-- largest_cluster <- which.max(table(comps$membership)) -->
<!-- exclude <- which(comps$membership != largest_cluster) %>% names() -->

<!-- tracts <- tracts %>%  -->
<!--     filter(!(GEOID %in% exclude)) -->

<!-- data <- data %>% -->
<!--     filter(tract %in% tracts$GEOID) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- b <- h_clust(tracts, data) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- k     <- 38 -->
<!-- g     <- spectral_cluster(g, sigma = sigma, k = k, nreps = 1000) -->
<!-- ``` -->

<!-- ```{r} -->

<!-- j <- 10 -->

<!-- m <- prominence_map(tracts, data) +  -->
<!--         guides(fill = FALSE)  -->

<!-- h <- h_clust_map(m, blocked_tracts, blocked_data, a, j, size_coef = .7) -->
<!-- h -->
<!-- ggsave(paste0('figs/mixed_', city,'.pdf'), width = map_width, height = map_height) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- f <- h_clust_map(m, tracts, data, b, j, size_coef = .7) -->
<!-- f -->
<!-- ggsave(paste0('figs/hclust_', city,'.pdf'), width = map_width, height = map_height) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- df %>%  -->
<!--     write_csv('figs/clustering_vals.csv') -->
<!-- loss_curves %>%  -->
<!--     write_csv('figs/loss_curves.csv') -->
<!-- MI %>%  -->
<!--     write_csv('figs/MI.csv') -->

<!-- ``` -->

<!-- ```{r} -->

<!-- gathered <- loss_curves %>%  -->
<!--     gather(key = type, value = val, -city, -k) %>%  -->
<!--     group_by(city, type) %>%  -->
<!--     mutate(val = cumsum(val)) %>%  -->
<!--     ungroup() -->

<!-- to_show <- c('Detroit', 'Chicago', 'Philadelphia') -->

<!-- MI_to_show <- MI %>%  -->
<!--     filter(city %in% to_show) -->

<!-- city <- NULL -->

<!-- labels <- gathered %>%  -->
<!--     filter(type == 'h_val', city %in% to_show) %>%  -->
<!--     group_by(city) %>%  -->
<!--     filter(val == max(val)) -->

<!-- labels$val <- labels$val + c(.04, -.05, -.06) -->
<!-- labels$k <- labels$k + c(-10, -2, 2) -->

<!-- gathered %>%  -->
<!--     filter(type == 'h_val', city %in% to_show) %>%  -->
<!--     ggplot() +  -->
<!--     geom_point(aes(x = k, y = val, color = city)) +  -->
<!--     geom_line(aes(x = k, y = val, color = city, group = city)) +  -->
<!--     geom_hline(aes(yintercept = I_XY, color = city), size = 1, data = MI_to_show, linetype = 'dashed') +  -->
<!--     theme_bw() +  -->
<!--     scale_color_brewer(palette = 'Accent') +  -->
<!--     ylab(expression(italic(I(C,Y)))) +  -->
<!--     xlab(expression(italic(k))) +  -->
<!--     ylim(c(0,NA)) +  -->
<!--     geom_label(aes(x = k, y = val, label = city, fill = city), data = labels) +  -->
<!--     scale_fill_brewer(palette = 'Accent') +  -->
<!--     guides(color = FALSE, fill = FALSE)  -->

<!-- ggsave('figs/loss_curves_h.pdf', height = map_height, width = map_width) -->

<!-- labels <- gathered %>%  -->
<!--     filter(type == 'm_val', city %in% to_show) %>%  -->
<!--     group_by(city) %>%  -->
<!--     filter(val == max(val)) -->

<!-- labels$val <- labels$val + c(.04, -.05, -.06) -->
<!-- labels$k <- labels$k + c(-10, -2, 2) -->

<!-- gathered %>%  -->
<!--     filter(type == 'm_val', city %in% to_show) %>%  -->
<!--      ggplot() +  -->
<!--     geom_point(aes(x = k, y = val, color = city)) +  -->
<!--     geom_line(aes(x = k, y = val, color = city, group = city)) +  -->
<!--     geom_hline(aes(yintercept = I_XY, color = city), size = 1, data = MI_to_show, linetype = 'dashed') +  -->
<!--     theme_bw() +  -->
<!--     scale_color_brewer(palette = 'Accent') +  -->
<!--     ylab(expression(italic(I(C,Y)))) +  -->
<!--     xlab(expression(italic(k))) +  -->
<!--     ylim(c(0,NA)) +  -->
<!--     geom_label(aes(x = k, y = val, label = city, fill = city), data = labels) +  -->
<!--     scale_fill_brewer(palette = 'Accent') +  -->
<!--     guides(color = FALSE, fill = FALSE)  -->

<!-- ggsave('figs/loss_curves_m.pdf', height = map_height, width = map_width) -->

<!-- ``` -->

>>>>

# knitr::read_chunk('R/utils.R')

source('R/utils.R')

@@

s <- s_clust_map(m, tracts, data, blocked_tracts, size_coef = .75)
s

@@

h <- h_clust_map(m, blocked_tracts, blocked_data, a, j, size_coef = .75)
h

@@

```{r}
f <- h_clust_map(m, tracts, data, b, j, size_coef = .75)
f
ggsave(paste0('figs/hclust_', city,'.pdf'), width = map_width, height = map_height)
```

@@

b <- h_clust(tracts, data)

g <- construct_information_graph(tracts = tracts, 
								 data = data, 
								 divergence = js_dist)

@@

```{r}
set.seed(1250)
k     <- 36
g     <- spectral_cluster(g, sigma = sigma, k = k, nreps = 1000)
```

@@

h <- h_clust_map(m, blocked_tracts, blocked_data, a, j, size_coef = .75)

@@

```{r}
city    <- 'Philadelphia'
in_data <- read_data(city, all_data)
data    <- in_data$data
tracts  <- in_data$tracts

set.seed(1234)
```

@@

h <- h_clust_map(m, blocked_tracts, blocked_data, a, j, size_coef = .75)
h
ggsave(paste0('figs/mixed_', city,'.pdf'), width = map_width, height = map_height)
```

```{r}
f <- h_clust_map(m, tracts, data, b, j, size_coef = .75)
f
ggsave(paste0('figs/hclust_', city,'.pdf'), width = map_width, height = map_height)
```

@@

# Loss Curves

labels <- data_frame(
    city = c('Detroit', 'Philadelphia', 'Chicago'),
    k    = c(20, 12, 32),
    I_XY   = c(.52, .3, .4)
)

loss_curves %>% 
    group_by(city) %>% 
    mutate(val = cumsum(h_val)) %>% 
    ggplot() + 
    geom_line(aes(x = k, y = val, color = city)) + 
    geom_point(aes(x = k, y = val, color = city)) + 
    theme_bw() + 
    scale_color_brewer(palette = 'Accent') + 
    scale_fill_brewer(palette = 'Accent') + 
    guides(color = FALSE, fill = FALSE) + 
    xlab(expression(italic(k))) + 
    ylab(expression(italic(I(C[k], Y)))) + 
    geom_hline(aes(yintercept = I_XY, color = city), data = MI, linetype = 'dashed', size = 1) + 
    geom_label(aes(x = k, y = I_XY, label = city, fill = city), data = labels) + 
    scale_y_continuous(lim = c(0, NA))

ggsave('figs/loss_curves_h.pdf', width = map_width, height = map_height)
```

labels <- data_frame(
    city = c('Detroit', 'Philadelphia', 'Chicago'),
    k    = c(20, 12, 32),
    I_XY   = c(.49, .25, .34)
)

loss_curves %>% 
    group_by(city) %>% 
    mutate(val = cumsum(m_val)) %>% 
    ggplot() + 
    geom_line(aes(x = k, y = val, color = city)) + 
    geom_point(aes(x = k, y = val, color = city)) + 
    theme_bw() + 
    scale_color_brewer(palette = 'Accent') + 
    scale_fill_brewer(palette = 'Accent') + 
    guides(color = FALSE, fill = FALSE) + 
    xlab(expression(italic(k))) + 
    ylab(expression(italic(I(C[k], Y)))) + 
    geom_hline(aes(yintercept = I_XY, color = city), data = MI, linetype = 'dashed', size = 1) + 
    geom_label(aes(x = k, y = I_XY, label = city, fill = city), data = labels) +
    scale_y_continuous(lim = c(0, NA))

ggsave('figs/loss_curves_m.pdf',  width = map_width, height = map_height)
```
